List of publications

### 2025-03-13 report/CONJ_COMD.qmd
template correction

			if (!is.null(outliers[[serie]]$ao_tc)) {
				cat(
					"\n\n- - *Additive outlier* (AO) associated to Trend-Cycle:",
					knitr::combine_words(format(zoo::as.yearmon(outliers[[serie]]$ao), "%B %Y")),
					"\n\n"
				)
			}

			if (!is.null(outliers[[serie]]$ls)) {
				cat(
					"\n\n- *Level shift* (LS):",
					knitr::combine_words(format(zoo::as.yearmon(outliers[[serie]]$ao), "%B %Y")),
					"\n\n"
				)
			}

>>>>

			if (!is.null(outliers[[serie]]$ao_tc)) {
				cat(
					"\n\n- - *Additive outlier* (AO) associated to Trend-Cycle:",
					knitr::combine_words(format(zoo::as.yearmon(outliers[[serie]]$ao_tc), "%B %Y")),
					"\n\n"
				)
			}

			if (!is.null(outliers[[serie]]$ls)) {
				cat(
					"\n\n- *Level shift* (LS):",
					knitr::combine_words(format(zoo::as.yearmon(outliers[[serie]]$ls), "%B %Y")),
					"\n\n"
				)
			}

### 2025-03-13 report/IPI.qmd
template correction

---
format: 
  html:
    toc: true
    number-sections: true
    embed-resources: true
    number-depth: 2
    other-links:
      - text: More surveys/data
        icon: patch-plus
        href: https://aqlt.github.io/publishTC.wp/
    code-links:
      - text: AQLT/publishTC.wp
        icon: github
        href: https://github.com/AQLT/publishTC.wp
date: today
date-format: long
params:
  file: "../data/IPI.yml"
execute:
  cache: true
author:
  - name: Alain Quartier-la-Tente 
    affiliation: LEMNA
    orcid: 0000-0001-7890-3857
comments: 
    hypothesis:
      theme: clean
echo: false
eval: true
---

@@

	cat("# ", spec_series[[serie]]$description, "\n")
	if (spec$plots$bymethods$enabled){
		cat("## ", spec$plots$bymethods$name)
		cat("\n\n::::: {.panel-tabset}\n")
		for (methods in names(last_est_s)) {
			cat(sprintf("\n### %s\n\n", gsub("\n", " ", methods)))
			first_date <- time(last_est_s[[methods]]$tc)[length(last_est_s[[methods]]$tc)] - spec$plots$nyears
			range_y <- range(window(ts.union(last_est_s[[methods]]$tc, last_est_s[[methods]]$x), start = first_date))
			cat(knitr::knit_child(text = c(
				"```{r}",
				"#| fig-height: 8",
				"#| fig-width: 8",
				'wrap_plots(all_plots[[methods]]) +
			plot_layout(axes = "collect") &
			theme_bw() & theme(legend.title = element_blank(), legend.position = "bottom") &
			# guides(color=guide_legend(nrow=nrow_legend)) &
			labs(x = NULL, y = NULL) &
			coord_cartesian(xlim = c(first_date, NA), y = range_y)',
			"```",
			""
			), envir = environment(), quiet = TRUE
			))
		}
		cat("\n:::::\n\n")
	}

@@

		cat("## ", spec$plots$byplots$name)
		cat("\n\n::::: {.panel-tabset}\n")
		for (plot in names(byplots)) {
			cat(sprintf("\n### %s\n\n", plot))
			first_date <- time(last_est_s[[1]]$tc)[length(last_est_s[[1]]$tc)] - spec$plots$nyears
			range_y <- range(window(ts.union(last_est_s[[1]]$tc, last_est_s[[1]]$x), start = first_date))
			cat(knitr::knit_child(text = c(
				"```{r}",
				"#| fig-height: 8",
				"#| fig-width: 8",
				'wrap_plots(byplots[[plot]]) +
			plot_layout(guides = "collect", axes = "collect") &
			theme_bw() & theme(legend.title = element_blank(), legend.position = "bottom") &
			labs(x = NULL, y = NULL) &
			coord_cartesian(xlim = c(first_date, NA), y = range_y) ',
			"```",
			""
			), envir = environment(), quiet = TRUE
			))
		}

@@

		cat("\n\n::::: {.panel-tabset}\n")
		for (methods in names(rev_data_s)) {
			cat(sprintf("\n### %s\n\n", gsub("\n", " ", methods)))
			first_date <- time(rev_data_s[[methods]])[length(time(rev_data_s[[methods]]))] - spec$plots$nyears
			range_y <- range(window(rev_data_s[[methods]], start = first_date), na.rm = TRUE)
			cat(knitr::knit_child(text = c(
				"```{r}",
				"#| fig-height: 8",
				"#| fig-width: 8",
				'autoplot(round(rev_data_s[[methods]], digits)) +
			theme_bw() + theme(legend.title = element_blank(), legend.position = "bottom") +
			labs(x = NULL, y = NULL) +
			coord_cartesian(xlim = c(first_date, NA), y = range_y)',
			"```",
			""
			), envir = environment(), quiet = TRUE
			))
		}

>>>>

---
format: 
  html:
    toc: true
    fig-format: png
    number-sections: true
    embed-resources: true
    number-depth: 2
    other-links:
      - text: More surveys/data
        icon: patch-plus
        href: https://aqlt.github.io/publishTC.wp/
    code-links:
      - text: AQLT/publishTC.wp
        icon: github
        href: https://github.com/AQLT/publishTC.wp
date: today
date-format: long
params:
  file: "../data/IPI.yml"
# execute:
#   cache: true
author:
  - name: Alain Quartier-la-Tente 
    affiliation: LEMNA
    orcid: 0000-0001-7890-3857
echo: false
eval: true
fig-height: 6
fig-width: 8
---

@@

	cat("# ", spec_series[[serie]]$description, "\n")
	if (spec$plots$bymethods$enabled){
		cat("## ", spec$plots$bymethods$name)
		cat("\n\n::::: {.panel-tabset}\n")
		for (i in seq_along(last_est_s)) {
		    methods <- names(last_est_s)[i]
			cat(sprintf("\n### %s\n\n", gsub("\n", " ", methods)))
			first_date <- time(last_est_s[[methods]]$tc)[length(last_est_s[[methods]]$tc)] - spec$plots$nyears
			range_y <- range(window(ts.union(last_est_s[[methods]]$tc, last_est_s[[methods]]$x), start = first_date))
			cat(knitr::knit_child(text = c(
				"```{r}",
				sprintf("#| label: bymethods-%s-%s", serie, studied_methods[i]),
				'wrap_plots(all_plots[[methods]]) +
			plot_layout(axes = "collect") &
			theme_bw() & theme(legend.title = element_blank(), legend.position = "bottom") &
			# guides(color=guide_legend(nrow=nrow_legend)) &
			labs(x = NULL, y = NULL) &
			coord_cartesian(xlim = c(first_date, NA), y = range_y)',
			"```",
			""
			), envir = environment(), quiet = TRUE
			))
		}
		cat("\n:::::\n\n")
	}

@@

		cat("## ", spec$plots$byplots$name)
		cat("\n\n::::: {.panel-tabset}\n")
		for (plot in names(byplots)) {
			cat(sprintf("\n### %s\n\n", plot))
			first_date <- time(last_est_s[[1]]$tc)[length(last_est_s[[1]]$tc)] - spec$plots$nyears
			range_y <- range(window(ts.union(last_est_s[[1]]$tc, last_est_s[[1]]$x), start = first_date))
			cat(knitr::knit_child(text = c(
				"```{r}",
				sprintf("#| label: byplots-%s-%s", serie, plot),
				'wrap_plots(byplots[[plot]]) +
			plot_layout(guides = "collect", axes = "collect") &
			theme_bw() & theme(legend.title = element_blank(), legend.position = "bottom") &
			labs(x = NULL, y = NULL) &
			coord_cartesian(xlim = c(first_date, NA), y = range_y) ',
			"```",
			""
			), envir = environment(), quiet = TRUE
			))
		}

@@

		cat("\n\n::::: {.panel-tabset}\n")
		for (i in seq_along(rev_data_s)) {
		    methods <- names(rev_data_s)[i]
			cat(sprintf("\n### %s\n\n", gsub("\n", " ", methods)))
			first_date <- time(rev_data_s[[methods]])[length(time(rev_data_s[[methods]]))] - spec$plots$nyears
			range_y <- range(window(rev_data_s[[methods]], start = first_date), na.rm = TRUE)
			cat(knitr::knit_child(text = c(
				"```{r}",
				"#| fig-height: 5",
				sprintf("#| label: revisions-%s-%s", serie, c("rav", studied_methods)[i]),
				'autoplot(round(rev_data_s[[methods]], digits)) +
			theme_bw() + theme(legend.title = element_blank(), legend.position = "bottom") +
			labs(x = NULL, y = NULL) +
			coord_cartesian(xlim = c(first_date, NA), y = range_y)',
			"```",
			""
			), envir = environment(), quiet = TRUE
			))
		}
